Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-03 contents/introduction.tex
Updates from ShareLaTeX

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-4}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-2}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textwidth}
            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-4}
    \end{subfigure}

>>>>

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.115\textheight}
            \includegraphics[height=2cm]{resources/MotivativeAnnotation/MPII}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textheight}
            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FashionPose}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.115\textheight}
            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FLIC}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.115\textheight}
            \includegraphics[height=2cm]{resources/MotivativeAnnotation/BBCPose}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
    \end{subfigure}
